\documentclass[a4paper]{article}

% Packages
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[margin=1.9cm]{geometry}
% parskip also adds a bit of space after each paragrah
\usepackage{parskip} % needed for un-doing paragraph indentation
\usepackage{physics}
%\usepackage{titlesec}

\usepackage[warnunknown, fasterrors, mathletters]{ucs}
\usepackage[utf8x]{inputenc}

% Always typeset math in display style
\everymath{\displaystyle}

% Use a larger font size
\usepackage[fontsize=14pt]{scrextend}

% Standard mathematical typesetting packages
\usepackage{amsfonts, amsthm, amsmath, amssymb}
\usepackage{mathtools}  % Extension to amsmath

% Symbol and utility packages
\usepackage{cancel, textcomp}
\usepackage[mathscr]{euscript}
\usepackage[nointegrals]{wasysym}

% Extras
\usepackage{physics}  % Lots of useful shortcuts and macros
\usepackage{tikz-cd}  % For drawing commutative diagrams easily
\usepackage{color}  % Add some colour to life
\usepackage{microtype}  % Minature font tweaks

% Common shortcuts
\def\mbb#1{\mathbb{#1}}
\def\mfk#1{\mathfrak{#1}}

\def\bN{\mbb{N}}
\def\bC{\mbb{C}}
\def\bR{\mbb{R}}
\def\bQ{\mbb{Q}}
\def\bZ{\mbb{Z}}

% Sometimes helpful macros
\newcommand{\func}[3]{#1\colon#2\to#3}
\newcommand{\vfunc}[5]{\func{#1}{#2}{#3},\quad#4\longmapsto#5}
\newcommand{\floor}[1]{\left\lfloor#1\right\rfloor}
\newcommand{\ceil}[1]{\left\lceil#1\right\rceil}

% Some standard theorem definitions
\newtheorem{Theorem}{Theorem}
\newtheorem{Proposition}{Theorem}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Corollary}[Theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{Definition}[Theorem]{Definition}



% Removes equation label numbers
\makeatletter
\renewcommand\tagform@[1]{}
\makeatother

% Theorems and stuff
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]
\newtheorem{exercise}{Exercise}[section]
\newtheorem{question}{Question}[section]


% Custom commands
\newcommand{\sectionSpace}{\vspace{2em}} % custom section break
\newcommand{\subsectionSpace}{\vspace{0.5em}}

%\setlength{\parindent}{0pt} % another way to have 0 paragraph indent
% \par for newlines works as well


\begin{document}
\title{INTENTIONALLY SCUFFED NOTES}
\author{Several Authors}
\maketitle
\newpage

%\normalsize % reset \Large{} text. Otherwise, put this into a frame


\begin{center}
    \Large 
    \textbf{
        REMEMBER THAT AT ANY POINT, THESE EQUATIONS, FORMULAE AND NOTES IN GENERAL MAY CONTAIN INTENTIONAL ERRORS. WE ARE NOT LIABLE FOR ANYTHING} 
\end{center}

\sectionSpace
\section{Introduction}
    Edit later.



\sectionSpace
\section{Proof by Induction}
    \subsection{The Principle of Mathematical Induction}
    When inducting, we must follow strict protocols. We first have the initial proposition (usually $P(1)$) where we must prove that LHS = RHS. Then we prove the kth case, then we assume the k+1th case to be true. 

    We can then conclude that by principle of mathematical induction, what we said is true because we proved and then assumed it to be. Simple as that.

    \subsectionSpace
    \subsection{Sequences and Series}



\sectionSpace
\section{Functions}
Let us focus on functions. 
    \subsection{Linear equation}
    A linear equation is a polynomial degree 1. It can be shown in several ways.
    \begin{itemize}
        \item General form: $ax + by = c$
        \item Slope-intercept form: $y = mx + c$
    \end{itemize}

    \subsectionSpace
    \subsection{Dealing With Infinity}
    For functions such as the inverse function ($1/x$), then $x$ cannot be zero otherwise we will have $1/0 = \infty$. 
    \begin{question}
        Why is $1/0 = \infty$?
    \end{question}


\sectionSpace
\section{Trigonometry}
    \subsection{Pythagorean Theorem}
    \[\sin^2\theta + \cos^2\theta= 1\]
    \[\tan^2\theta + 1 = \sec^2\theta\]
    \[\cot^2\theta + 1 = \csc^2\theta\]

    \subsectionSpace
    \subsection{Angle Sum and Difference}
    $$\sin(A \pm B) = \sin A \cos B \pm \cos A \sin B$$
    $$\cos(A \pm B) = \cos A \cos B \pm \sin A \sin B$$

    \subsectionSpace
    \subsection{Double Angle Identities}
    Double angle identities are derived from the angle and sum difference equations. 

    We know that
    $$\sin(2x) = 2\sin(x)\cos(x)$$
    therefore, we can say that
    $$\sin(4x) = 4\sin^2(x)\cos^2(x)$$

    \subsectionSpace
    \subsection{$n$ Angle Identities}
    Using De Moivre's theorem it is known that
    \begin{align}
        (|z|\cos{\theta})^n=|z|^n\cos{n\theta}
    \end{align}
    The identity $\cos{\theta}=\sin{\left(\frac{\pi}{2}-\theta \right)}$ can be applied to deduce identites for $\sin$.
    \begin{align}
        \left(|z|\sin{\left(\frac{\pi}{2}-\theta \right)}\right)^n=|z|^n\sin{\left(\frac{\pi}{2}-\theta \right)}
    \end{align}
    Since the unit circle has radius 1, $z=1$. Hence, the following identities are derived.
    \begin{align}
        \cos{n\theta}=(|n|\cos{\theta})^n\qquad \sin{n\theta}=\left(|n|\sin{\left(\frac{\pi}{2}-\theta \right)}\right)^n
    \end{align}
    How useful!



\sectionSpace
\section{Limits}
    \subsection{Trigonometric Limits}
    $$\lim_{\theta \to 0} \frac{\sin(\theta)}{\theta} = 1$$

    $$\lim_{\theta \to 0} \sin^{\theta}(\theta) = 1$$

    \[\lim_{\theta \to \infty} \sin^{\theta}(\theta) = 0\]

    \begin{question}
        What would $\lim_{\theta \to 0} \cos^{\theta}(\theta)$ be equal to?
    \end{question}

\sectionSpace
\section{Calculus of the Differential Kind}
    \subsection{Deriving from First Principles}
    Deriving from first principles is the fundamentals of calculus. In fact, we refer to this as the fundamental theorem of calculus.

        \subsubsection{First Principles with $\sin(x)$}
        Recall the formula for first principles:
        \[f'(x) = \lim_{h \to 0} \frac{f(x+h) - f(x)}{h}\]
        \begin{align}
            \dv{\sin(x)}{x} & = \lim_{h \to 0} \frac{\sin(x+h) - \sin(x)}{h} \\
            & = \lim_{h \to 0} \frac{\sin{x}\cosh + \cos{x}\sinh - \sin{x}}{h} \\
            & = \lim_{h \to 0} \frac{\sin{x}(\cosh - 1) + \cos{x}\sinh}{h} \\
            & = \sin{x}\lim_{h \to 0}\frac{\cosh - 1}{h} + \cos{x}\lim_{h \to 0} \frac{\sinh}{h} \\
            & = \cos{x}
        \end{align}


\sectionSpace
\section{Integration}
    \subsection{Integration Rules}
    $$\int k\,\dd{x} = kx + C$$
        \subsubsection{The Sum Rule}
        $$\int i + j + k\,\dd{x} = \int i\,\dd{x} + \int j\,\dd{x} + \int k\,\dd{x} = ix + jx + kx + 3C$$

        \subsubsection{The Difference Rule}
        Similar to the sum rule, the difference rule is essentially the sum of additive inverses:
        $$\int i - j - k\,\dd{x} = \int i\,\dd{x} - \int j\,\dd{x} - \int k\,\dd{x} = ix - jx - kx - 3C$$

    \subsectionSpace
    \subsection{Substitution}
    
    \subsectionSpace
    \subsection{By Parts (Product Rule)}
    Integration by parts is when you split it to solve by parts. Suppose we have a function $f(x) = u(x)v(x)$ which we want to find the integral of:
    $$\int f(x) \,\dd{x} = \int u(x)v(x) \,\dd{x}$$
    We can use integration by parts, also known as the product rule of integrals:
    $$\int u(x)v(x)\,\dd{x} = \int u(x)\,\dd{x}\times \int v(x)\,\dd{x}$$

    \begin{exercise}
        Solve $\int x^2\,\dd{x}$ using integration by parts.
    \end{exercise}



\sectionSpace
\section{Complex Numbers}
    \subsection{Euler's Form}
    We know that
    $$\sin^2\theta + \cos^2\theta = 1$$
    We also know the famous equation known as Euler's formula. The imaginary number one. With the pi. No, not the one with polyhedrons. To be more precise, we mean Euler's identity, the ``beautiful" equation.
    $$e^{i\pi} + 1 = 0$$

    Therefore, we can then conclude that:
    $$e^{i\theta} + \sin^2\theta + \cos^2\theta = 0$$
    $$\frac{e^{i\theta} + \sin^2\theta}{-\cos^2\theta} = 1$$
    $$-\frac{e^{i\theta}}{\cos^2\theta} -\frac{\sin^2\theta}{\cos^2\theta} = 1$$
    $$-e^{i\theta}\sec^2\theta -\tan^2\theta = 1$$
    $$-e^{i\theta}\sec^2\theta = 1 + \tan^2\theta$$
    $$-e^{i\theta}\sec^2\theta = \sec^2\theta$$
    $$-e^{i\theta} = 1 \Rightarrow e^{i\theta} = -1$$

    What a beautiful conclusion!

\subsection{The Cauchy-Riemann Equations (11 Essential Maths Topic)}
The Cauchy-Riemann Equations state that $\forall f:\mathbb{C}\to\mathbb{C}$ where $f:x+iy\mapsto u(x,y)+v(x,y)$:
$$f \text{ is holomorphic}\Leftrightarrow \frac {\partial u}{\partial x}=\frac {\partial v}{\partial y} \text { and }\frac {\partial u}{\partial y}=-{\frac {\partial v}{\partial x}}$$
The Cauchy-Riemann Equations can also be written using Wirtinger derivatives, which are defined as follows:
$$\frac {\partial }{\partial z}={\frac {1}{2}}\left({\frac {\partial }{\partial x}}-i{\frac {\partial }{\partial y}}\right)$$
$${\frac {\partial }{\partial {\bar {z}}}}={\frac {1}{2}}\left({\frac {\partial }{\partial x}}+i{\frac {\partial }{\partial y}}\right)$$
Therefore, it is trivial to see that for any holomorphic function $f$:
$${\frac {\partial }{\partial {\bar {z}}}}=0$$
\begin{exercise}
    Prove the Cauchy-Riemann Equations using first principles.
\end{exercise}

\sectionSpace
\section{Linear Algebra}
    \subsection{Equation of a line}
    Linear algebra is named after its most important mathematical object, the linear algebruh function.\\\\
    As you already know, linear function can be written using the slope-intercept form $y=ax+b$.\\\\
    The $a$ determines the slope of the line and $b$ determined the $y$-intercept.

\end{document}
